Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
updated results section

%% Check what willy wrote.
%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.

Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.

@@

After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.

>>>>

%% Check what willy wrote.
%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
In order to answer RQ1, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}. Initially we created predictions of the changes from inspecting the source code and accompanying documentation. Following the interview we compared our results with response from the interview to decide the actual maintenance categories of the changes. \ref{table:Categories} shows the predicted and actual maintenance categories.

The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. New and modified concern additions or modifications to modules, removed are features which have been removed entirely without deprecating and general trends are broad changes which do not directly affect functionality.

@@

After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
